\begin{thebibliography}{1}
\bibitem{Pardela} A. Sokołowski, T. Pardela (2014). Application of Fourier Transforms in Classification of Medical Images. Advances in Intelligent Systems and Computing, 193-200.

\bibitem{Dogra} Ayush Dogra, Parvinder Bhalla (2014). Image Sharpening By Gaussian And Butterworth High Pass Filter. Department of ECE, Maharishi Markandeshwar University, Mullana, Ambala, India. Biomed Pharmacol J. 

\bibitem{Dogra} Chris Dogra, John Wiley, Sons (2007). Fundamental Principles of Optical Lithography: The Science of Microfabrication. 

\bibitem{Cooley} Cooley, James W.; Tukey, John W. (1965). An algorithm for the machine calculation of complex Fourier series. Math. Comput. 19 (90), 297–301.

\bibitem{Popa} Călin-Adrian Popa, Cosmin Cernăzanu-Glăvan (2018). Fourier Transform-Based Image Classification Using Complex-Valued Convolutional Neural Networks. International Symposium on Neural Networks (ISNN). Minsk, Belarus.

\bibitem{Daniel} Daniel B. Rowe, Andrew S. Nencka, Raymond G. Hoffmannb (2007). Signal and noise of Fourier reconstructed fMRI data. J Neurosci Methods, 361–369.

\bibitem{Escofet} Escofet, J., Millan, M.S. and Rallo, M. (2001). Applied Optics, Volume 40, Issue 34, pp. 6170-6176.

\bibitem{Granlund} G. H. Granlund (1972). Fourier processing for handwritten character recognition. IEEE Trans. Comput., vol. C-21, no. 3, pp. 195-201.

\bibitem{Harte} Harte, T.P. and Hanka R. (1997). Number Theoretic Transforms in Neural Network Image Classification.

\bibitem{Pharr} I. Pharr, Matt. II. Fernando, Randima (2005). Medical Image Reconstruction with the FFT. GPU gems 2. NVIDIA Corporation.

\bibitem{Levchenko} Levchenko, E.B., Myl’nikov, G.D., Timashev, A.N. and Turygin, A.Y. (1992). Neural network for image Fourier transform classification. Neuroinformatics and Neurocomputers, RNNS/IEEE Symposium. Vol. 1, pp 196-207.

\bibitem{Li} Li C.T., Wilson, R. (1995). Image Segmentation Using Multiresolution Fourier Transform. Department of Computer Science, University of Warwick.

\bibitem{Li} Li, J., Chen, L., \& Cai, Y. (2009). Dynamic Texture Segmentation Using 3-D Fourier Transform. 2009 Fifth International Conference on Image and Graphics. 

\bibitem{Li} Li-Wei Yang, Xiao-Feng Wang (2012). Leaf Image Recognition Using Fourier Transform Based on Ordered Sequence. ICIC 2012: Intelligent Computing Technology, pp 393-400.

\bibitem{Mohammed} Mohammed H. Rasheed, Omar M. Salih, Mohammed M. Siddeq, Marcos A.Rodrigues (2020). Image compression based on 2D Discrete Fourier Transform and matrix minimization algorithm. Elsevier Inc.

\bibitem{Efford} Nick Efford (2000). Digital Image Processing: A Practical Introduction Using JavaTM. Chapter 11: Morphological image processing. Pearson Education.

\bibitem{Paquet} Paquet, Eric, Rioux, Marc, Arsenault, Henri H. (1993). Range image segmentation using the Fourier transform. Optical Engineering 32(09), 2173-2180.

\bibitem{Rafael} Rafael C. Gonzalez, Richard E. Woods (2008). Digital Image Processing 3rd Edition.

\bibitem{Robert} Robert, P. (1980). Performance of the Discrete Fourier Transform Satellite Imagery Classification Technique. SYSTEMS AND APPLIED SCIENCES CORP RIVERDALE MD.

\bibitem{Shubing} Shubing Wang (2007). Applications of Fourier Transform to Imaging Analysis. 

\bibitem{Tang} Tang X. and Stewart W.K. (2000). Optical and Sonar Image Classification: Wavelet Packet Transform vs Fourier Transform. Computer Vision and Image Understanding, Volume 79, Number 1,
pp. 25-46(22).

\bibitem{Weisstein} Weisstein, Eric. Convolution Theorem. MathWorld.

\bibitem{Wu} Wu, H.S., Barba, J., Gil J. (1996). An iterative algorithm for cell segmentation using short-time Fourier transform. J Microsc. 184(Pt 2), 127-32.

\end{thebibliography}